What's in a name? On the automated topic naming of software maintenance activities

### 2010-03-06 icpc/icpc2010.tex
wording fixes
answered the research questions

>>>>

\paragraph{Do label frequencies change over time?} Yes, MySQL's label
frequencies decreased as it got older. Usability and reliability
labels became more and more infrequent as it matured. Maintainability topics
became more prevalent as MaxDB matured.

\paragraph{Do the different projects differ in their relative topic
  interest?} Yes they do, MySQL 3.23 had more proportionally more
functionality labelled topics while MaxDB had proportionally more
efficiency and portability related topics.
